Experimental Analysis of a Spatialised Audio Interface for People with Visual Impairments

### 2020-01-23 paper.tex
Added adaptation notes to figures
More edits

\begin{abstract}
  Sound perception is a fundamental skill for many people with severe sight impairments.
  The research presented in this paper is part of an ongoing project, the aim of which is to build a mobile guidance aid to assist people with vision impairments find objects within an unknown indoor environment.
  This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids. 
\end{abstract}

@@

The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:tango-headphone}).
This Tango device uses a set of embedded RGB-D cameras that provide access to powerful real-time localisation, through IMU measurements and landmark tracking, and image-processing capabilities.
It also gives access to Android's full range of interface and I/O options.
Unlike normal headphones, bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
These headphones have the benefit of not interfering with a user's normal hearing function.

%The prototype is based on a Google Project Tango\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)} device, pictured in \cref{fig:tango-headphone}, that embeds a colour camera and provides access to powerful real-time localisation (through IMU measurements and landmark tracking) and image-processing facilities. 
%It also provides access to Android's full range of interface tools and I/O options. 
%Furthermore, a set of bone-conduction headphones (see \cref{fig:tango-headphone}), which are placed on a user's cheekbones instead of their ears and do not interfere with normal hearing, are used to transmit the audio signals to the user.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and the bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right). Adapted from~\citet{lock2019bone}.}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

This system's guidance instructions can be interpreted in real-time without posing a significant cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

The rest of the paper starts by discussing previous relevant works and research in \cref{sec:prev-work}, followed by a presentation of the design and implementation of our interface in \cref{sec:system-description}.
This is followed by a description of the experiments that were conducted and a discussion of their results in \cref{sec:experiments} and \cref{sec:results}.
Finally, the paper concludes with a summary and discussions on future research prospects in \cref{sec:conclusion}.

@@

Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments.
Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.
Indeed, participants report that they prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

%\todo{edit start}
%Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
%The majority of these systems rely on one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
%In general, participants with visual impairments report that they prefer haptic and vocal feedback out of the three options~\citep{arditi2013user}.
%However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
%Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
%Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions~\citep{arditi2013user}.
%Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.
%\todo{edit stop}

@@

%Simple audio tones and vocal feedback signals have been used in conjunction with cameras and object detectors to communicate their relative positions to the user with a reasonable level of accuracy~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.
%Following this, researchers have investigated using audio signals that are spatialised with a head-related transfer function (HRTF), simulating a sound source located at some arbitrary 3D position~\citep{geronazzo2016interactive,wilson2007swan,katz2010navig,blum2013spatialized}.
%The authors generally report favourable results for this guidance approach when used with standard over-ear headphones or speakers. 
%However, other authors have found that the choice of audio transmission medium can have a significant effect on performance.
%Cheaper headphones and bone-conduction headphones generally report unfavourable results when compared to over-ear or more expensive alternatives~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}. 
%This seems to be limited to the elevation dimension, however, and can be improved with HRTFs adjusted for the bone-conduction pathway~\citep{stanley2006lateralization}.
%~\citet{durette2008visuo} transmit a target's elevation angle by adjusting the signal's pitch and report favourable results. 
%We extended on the latter's work and investigated spatial audio for guidance mode closely in an initial study and found that it is indeed able to adequately guide a user towards a target area~\citep{lock2019bone}.
%We expand upon this preliminary study with a more thorough investigation into the participants' performance and how changes to the audio signal's behaviour can impact that performance.

@@

Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
%To address these issues, we implemented a handheld mobile system using a Google Tango device that is able to localize itself in real-time.
To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.

@@

Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound,lock2019bone}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

@@

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated in previous work~\citep{lock2019bone}.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis~\citep{lock2019bone}. }
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound,lock2019bone}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume compared to the left ear.

@@

A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison,lock2019bone}.
To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
When the camera vector is at the correct elevation, the tone pitch is set to neutral.
When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\citep{pratt1930spatial,blauert1997spatial}.
An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\citep{shepard1964circularity}.
The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.

The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}) and the gradient is determined by setting the angle and pitch limits.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
After practical tests with the interface, we set the neutral, on-target pitch the HMI emits to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.

@@

A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of information flow.
The system implementation used here is similar to the one used by~\citet{lock2019bone}.
When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
The audio generator then produces a tone based on the difference between the device and the target's positions.
The tone is sent to the audio output channel, which plays it back to the user.
A WiFi recording module is constantly monitoring the different values of the device's parameters and of the target's position, as well as the system's output, recording everything in a remotely stored datafile.

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal~\citep{lock2019bone}. }\label{fig:pipeline}
  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
\end{figure}

@@

%To test the interface's effectiveness at guiding the user in a pointing task, a set of experiments were conducted to capture the difference between the targets' actual direction and the directions the participants' perceived them to be.
%The participants were given a Tango device running an app that implements the experimental setup in \cref{fig:pipeline}. The app generates a set of virtual targets and presents them to each participant through the audio interface, one at a time. 
%The targets are generated at a constant distance from the participant and their pan and elevation angles are uniformly generated across the four quadrants of the pan-elevation plane to avoid clustering.
%Each target's angular position is adjusted and communicated in real-time as the participant points the device around. 
%When the participants were confident that the device was on-target, i.e.~hearing the audio front-on at \SI{512}{\hertz}, they tapped the screen, marking the location and generating the next target.
%The targets' positions are all set relative to the device's coordinate system, which is tracked using the Tango hardware and localisation API.\
%A total of 28 targets were generated per participant.

This experimental setup was used in~\cite{lock2019bone}.
However, in these experiments we also want to see how changing the gradient of the pitch function, visualised in \cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively, giving pitch intervals of

@@

Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
It can also be used to improve the interface's frequency profile and performance. 
\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.
%The median is used for each grouping given the skewed plot and

@@

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
%while Group~\textit{G2} has 2 significantly different levels of performance between the \textit{lo} and \textit{med} settings, as well as for the \textit{med} and \textit{hi} settings ($p_{lo-med} = 0.011, p_{med-hi} = 0.001$).
We also noted that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset.

@@

%\subsection{Participant Feedback}

%\todo{include subjective feedback?}

>>>>

\begin{abstract}
  Sound perception is a fundamental skill for many people with severe sight impairments.
  The research presented in this paper is part of an ongoing project with the aim to create a mobile guidance aid to help people with vision impairments find objects within an unknown indoor environment.
  This system requires an effective non-visual interface and uses bone-conduction headphones to transmit audio instructions to the user.
  It has been implemented and tested with spatialised audio cues, which convey the direction of a predefined target in 3D space.
  We present an in-depth evaluation of the audio interface with several experiments that involve a large number of participants, both blindfolded and with actual visual impairments, and analyse the pros and cons of our design choices.
  In addition to producing results comparable to the state-of-the-art, we found that Fitts's Law for predicting human movement can be used to form a metric that can be used to improve and refine the quality of the audio interface in future mobile navigation aids. 
\end{abstract}

@@

The hardware used for the guidance system prototype are a Google Project Tango device\footnote{https://en.wikipedia.org/wiki/Tango\_(platform)}, along with a set of bone-conducting headphones (both are shown in \cref{fig:tango-headphone}).
This Tango device uses a set of embedded RGB-D cameras and other hardware and software components to provide accurate real-time localisation estimates and has powerful image-processing capabilities.
It also gives access to Android's full range of interface and I/O options.
Unlike normal headphones, bone-conducting headphones are placed on and conduct audio signals through a user's cheekbones, instead of their ear canal.
These headphones have the benefit of not interfering with a user's normal hearing function.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:tango-headphone}\includegraphics[width=0.5\columnwidth]{figures/tango_tablet_headphone_edit.pdf}}
~
  \subfloat[]{\label{fig:participant}\includegraphics[width=0.24\columnwidth]{figures/vi_participant.pdf}}
  \caption{A Tango tablet and bone-conduction headphones, the primary hardware components used in this work (left), and a participant with visual impairments using the system during an experiment (right). Adapted from~\citet{lock2019bone}.}
  \Description{The Tango tablet and the bone-conduction headphones, the primary hardware components used in this work, and a participant with visual impairments using the system during an experiment.}
\end{figure}

The system generates guidance instructions that can be interpreted in real-time with minimal additional cognitive load to the user, given humans' natural ability to determine a sound source's 3D position.
By adjusting a tone's spectral make-up (elevation angle), time delay and level difference (pan angle), and intensity (distance), a sound source can be spatialised to come from an arbitrary location.
In this case, only the pan and elevation angles are given to the user to instruct them to point the camera towards a target object or visual feature.
However, the spectral signature generated by bone-conduction headphones cannot properly be interpreted by a human, since they are placed on the user's cheekbones and bypass the ear's outer structure.
We address this limitation by having the system convey the target's elevation angle by adjusting the tone's pitch instead of spatialising it in the elevation dimension.
In previous work, we showed that this audio signal transmission scheme can direct users to a target position with a degree of accuracy comparable to fully spatialised signals used with expensive closed-cup headphones.
These results were presented at the 9th International Workshop on Assistive Engineering in 2019~\citep{lock2019bone}.
We expand upon this initial investigation with a larger dataset and look at if, and how, changing the behaviour of the pitch affects target acquisition performance in terms of time and angular error.
The participants' hearing characteristics are also measured to determine if there are limitations to how well they can determine audio pitch or direction.

@@

The rest of the paper starts by discussing relevant works and previous research in \cref{sec:prev-work}.
This is followed by a discussion on the design and implementation of our interface in \cref{sec:system-description}.
The experiments that were conducted are discussed in \cref{sec:experiments}, while their results are presented and discussed in \cref{sec:results}.
The paper concludes with a summary of the work and discussions on future research prospects in \cref{sec:conclusion}.

@@

Over the years, commercial and academic groups have devised new and innovative mobile navigation and travel aids for people with visual impairments.
Many of these systems make use of one or a combination of vocal~\citep{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\citep{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\citep{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to present a user with guidance instructions, each of which has its own set of features and limitations.
Out of these three options, respondents with visual impairments typically prefer haptic and vocal feedback~\citep{arditi2013user}.
However, from an ergonomic perspective, haptic feedback has significant shortcomings and require additional external hardware to transmit guidance instructions with sufficient resolution.
Furthermore, both haptic and vocal feedback can present a cognitive burden and overwhelm a user's input bandwidth, particularly when high-resolution guidance is required.

Indeed, \citet{arditi2013user} reports that users prefer controlling the rate at which guidance signals are presented to them, instead of being given constant guidance. 
As an alternative, simple audio tones are less prone to these bandwidth and hardware limitations.
However, such tones can potentially fatigue a user if there are too unpleasant.
Researchers have started using cameras and object detectors to determine what a user is looking at and then use simple audio tones and vocal feedback signals to indicate to the user where to find an object.
They report favourable results with these systems~\citep{schauerte2012assistive,tian2013computer,fiannaca2014headlock,vazquez2012helping}.

@@

@@

Existing electronic navigation aids have typically struggled to gain market traction and replace the traditional walking cane as the standard assistive tool for people with visual impairments.
Current technological limitations include prohibitive costs, bulky hardware requirements and non-user-friendly interfaces~\citep{golledge2004stated,yusif2016older,arditi2013user}.
To address these issues, we implemented a handheld mobile system that is based on a concept proposed by~\citet{lock2019active} and tested by~\citet{lock2019bone} using a Google Tango device that is able to localise itself in real-time.
This system has the benefit of minimal hardware requirements and a compact, familiar form-factor, which will help to overcome the hurdle of user-acceptance and usability.

@@

Humans localise a sound source in three dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\citep{blauert1997spatial,blauert1969sound}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one.

@@

The guidance information is presented to the user in terms of pan and elevation angles, indicating the angular adjustments required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\citep{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle, instead, can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones~\citep{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization,lock2019bone}. 
This interface was implemented and evaluated by~\citet{lock2019bone}.

\begin{figure}
  \centering
  \subfloat[]{\label{fig:cam-coords}\includegraphics[width=0.3\columnwidth]{figures/camera_coordinate.pdf}}
~
  \subfloat[]{\label{fig:pitch-gain}\includegraphics[clip, trim=0 0 0 40, width=0.7\columnwidth]{figures/pitch_gain_function.png}}
  \caption{The reference system used by the guidance interface showing the camera vector and pan and elevation angles (left) and the pitch gain function used to convey the target's elevation angle (right). Note the logarithmic scale of the frequency axis. Adapted from~\citet{lock2019bone}. }
  \Description{The reference system used by the guidance interface showing the camera vector and pan and elevation angles and the pitch gain function used to convey the target's elevation angle. Note the logarithmic scale of the frequency axis. }
\end{figure}

@@

The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\citep{blauert1969sound}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right will hit the right ear first with a slightly higher volume compared to the left ear.

@@

A generic HRTF implementation with bone-conduction headphones is not very effective in conveying the elevation angle of a sound source~\citep{macdonald2006spatial,schonstein2008comparison}.
To compensate for this, we communicate the target's elevation angle by adjusting the tone's pitch (i.e.\ the sine wave's frequency) as a function of the elevation. 
When the camera vector is at the correct elevation, the tone pitch is set to neutral.
When the target is above or below the camera vector, the pitch is increased or decreased, respectively.
This high/low association scheme is motivated by humans' natural association of high-pitched sounds with elevated sound sources, and low-pitched sounds with source's below the individual's earline~\citep{pratt1930spatial,blauert1997spatial}.
An octave- and semitone-based function is used to adjust the tone's pitch to ensure perceptible changes, while keeping the timbre roughly constant~\citep{shepard1964circularity}.
The pitch is updated at a rate of \SI{10}{\hertz} and changes as the user moves the device.

The pitch is changed as a linear function of the elevation angle (see \cref{fig:pitch-gain}) and the gradient is determined by setting the angle and pitch limits.
For this work, we only consider a \SI{180}{\degree} field of view in front of the user and limit the elevation angle to a range of \SI{\pm90}{\degree}, or $[-\frac{\pi}{2}, \frac{\pi}{2}]$.
After practical tests with the interface, we set the neutral, on-target pitch the HMI emits to \SI{512}{\hertz}, which is comfortably audible and allows for a large number of suitable octave limits to be selected.
The pitch limits are set at some integer number of octaves above and below the neutral, on-elevation pitch.
In previous tests with this specific interface, its performance was comparable to normal over-ear headphones transmitting a spatialised signal that transmits the elevation angle~\cite{lock2019bone}.

@@

A diagram of the experimental system pipeline is shown in \cref{fig:pipeline}, where the arrows indicate the direction of information flow.
The system implementation used here is similar to the setup used by~\citet{lock2019bone}.
When the user taps the Tango's screen, a new virtual target is generated and its coordinates are sent to the audio generation module, along with the device's current position and orientation.
The audio generator then produces a tone based on the difference between the device and the target's positions.
The tone is sent to the audio output channel, which plays it back to the user.
A WiFi recording module is constantly monitoring the different values of the device's parameters and of the target's position, as well as the system's output, recording everything in a remotely stored datafile.

\begin{figure}
  \centering
  \includegraphics[clip=true, trim=0 120 80 50, width=0.8\columnwidth]{figures/pipeline.pdf}
  \caption{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. Adapted from~\citet{lock2019bone}. }\label{fig:pipeline}
  \Description{A diagram of the individual system components and their communication pipelines. $F$ indicates a feedback signal and $P$ a pose signal. }
\end{figure}

@@

A similar experimental setup was used in~\cite{lock2019bone}.
However, in these experiments we also want to see how changing the gradient of the pitch function, visualised in \cref{fig:pitch-gain}, affects target acquisition performance, e.g.\ does a steeper pitch gain as a function of the elevation angle improve accuracy or decrease the search time?
Pitch limits of one, two and three octaves above and below the neutral tone were then set for the so-called \textit{lo}, \textit{med} and \textit{hi} pitch gradient settings respectively, giving pitch intervals of

@@

Assuming these differences are normally distributed, we fit a cumulative distribution function (CDF) over each participant's set of results for their correct guesses.
We then used each CDF's parameters to determine a frequency cut-off threshold, where the participant could not longer reliably tell tones apart, which is set to contain 75\% of each participant's correct guesses.
The median of these threshold values can then be used to estimate the frequency difference at which the entire participant population can no longer tell the difference between two tones. 
It can also be used to improve the interface's frequency profile and performance. 
\cref{fig:pitch-thresholds} shows the threshold distribution, along with the median value, which was found to be approximately 0.4 semitones for each group. 
\cref{fig:pitch-thresholds-hist} contains histograms of the cut-off frequency thresholds for each setting, which show that the settings can be grouped together.

@@

A post-hoc analysis using the Wilcoxon signed rank test, with a Holm-Bonferroni correction applied to the commonly used 0.05 threshold, was used to investigate the setting relationships more closely. 
This analysis reveals that there is a significant difference between the errors generated by the \textit{lo} and \textit{med} settings, as well as the \textit{lo} and \textit{hi} settings, for Group~\textit{G1} ($p_{lo-med} = 0.003,~p_{lo-hi} < 0.001$), showing that the \textit{lo} setting clearly produces the highest error, while it is not clear which one of the \textit{med} and \textit{hi} settings is better for Group~\textit{G1}. 
Based on the current data, it is impossible to conclude which setting produces the smallest angular error for Group~\textit{G2}, but this may because of the relatively small sample size for each setting. 
We also noted that there is a significant negative error bias in the elevation data for all the settings and groups, possibly caused by a cognitive constraint introduced by the floor, below which the participants believed the targets could not appear.
Since this bias seems to be constant, it could be easily addressed in a future version of the audio interface by adjusting its frequency parameters to shift the bias upwards by a constant offset.

@@
